MPA Gap Analysis: IUCN and AquaMaps

### 2016-05-18 case_study_mpa/3_mpa_spp_analysis.Rmd
updated to Mazu to rerun the figures.

dir_N <- c('Windows' = '//neptune.nceas.ucsb.edu/data_edit',
           'Darwin'  = '/Volumes/data_edit',
           'Linux'   = '/var/data/ohi')[[ Sys.info()[['sysname']] ]]

@@

dir_anx <- file.path(dir_N, 'git-annex/globalprep/SPP_ICO')
dir_fig <- file.path(dir_git, 'figures')
dir_data <- file.path(dir_git, 'data')
dir_am_data <- file.path(dir_N, 'git-annex/globalprep/_raw_data/aquamaps/v2015/csv')

@@

print(barchart_mpa_gap)
ggsave(plot = barchart_mpa_gap,
       filename = file.path(dir_fig, 'fig4_barchart_mpa_gap.png'),
       width = 11.4, height = 5, units = 'cm')
ggsave(plot = barchart_mpa_gap,
       filename = file.path(dir_fig, 'fig4_barchart_mpa_gap.tif'), device = 'tiff',
       width = 11.4, height = 5, units = 'cm')

>>>>

dir_M             <- c('Windows' = '//mazu.nceas.ucsb.edu/ohi',
                       'Darwin'  = '/Volumes/ohi',    ### connect (cmd-K) to smb://mazu/ohi
                       'Linux'   = '/home/shares/ohi')[[ Sys.info()[['sysname']] ]]

@@

dir_anx <- file.path(dir_N, 'git-annex/globalprep/SPP_ICO')
dir_fig <- file.path(dir_git, 'figures')
dir_data <- file.path(dir_git, 'data')
dir_am_data <- file.path(dir_N, 'git-annex/globalprep/_raw_data/aquamaps/d2015/csv')

@@

print(barchart_mpa_gap)
ggsave(plot = barchart_mpa_gap,
       filename = file.path(dir_fig, 'fig4_barchart_mpa_gap.png'),
       width = 11.4, height = 5, units = 'cm', dpi = 600)
ggsave(plot = barchart_mpa_gap,
       filename = file.path(dir_fig, 'fig4_barchart_mpa_gap.tif'), device = 'tiff',
       width = 11.4, height = 5, units = 'cm', dpi = 600)
